---
title: "**Supplementary Information**"
subtitle: "BIOREDIS: rapid and customizable design of nucleic acid therapeutics"
output: pdf_document
---

\



```{r include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}

data <- readxl::read_excel('optimization_results.xlsx')


```


```{r include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}


data2_KIT <- readxl::read_excel('mutual_KIT.xlsx')
data2_PAX <- readxl::read_excel('mutual_PAX3.xlsx')


```


# Supplementary Tables


## Codons optimisation



```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(tidyverse)

df <- data[,c('tool','gene', 'GC', 'freq', 'changed_bases %' , 'changed_codons %', 'MFE [kcal/mol]')]

knitr::kable(df)


```

**Table S1:** Data including statistics of the native sequences (*KIT, PAX3*) and optimized sequences generated using various tools.


\


```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(tidyverse)

df <- data2_KIT[,c('source', 
                   'RNAi_seq', 
                   'specificity', 
                   'GC%', 
                   'score')]

knitr::kable(df)

```

**Table S2:** Data including statistics of the predicted RNAi of *KIT* gene using various tools.

 \newpage



```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(tidyverse)

df <- data2_PAX[,c('source', 
                   'RNAi_seq', 
                   'specificity', 
                   'GC%', 
                   'score')]

knitr::kable(df)


```

**Table S3:** Data including statistics of the predicted RNAi of *PAX3* gene using various tools.



\newpage



# Supplementary Figures


```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.1-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.1-PAX3.pdf")


```


**Figure S1.** Percent of nucleotide changes in optimised sequences relative to the native sequence of the *KIT* and *PAX3* genes.

\newpage






```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.2-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.2-PAX3.pdf")

```


**Figure S2.** Percent of codon changes in optimised sequences relative to the native sequence of the *KIT* and *PAX3* genes.

\newpage






```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.3-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.3-PAX3.pdf")


```


**Figure S3.** Codon frequency values in optimised and native sequences of the *KIT* and *PAX3* genes

\newpage




```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.4-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.4-PAX3.pdf")


```


**Figure S4.** GC content [%] in optimised and native sequences of the *KIT* and *PAX3* genes

\newpage




```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

knitr::include_graphics("supplemetary_figures/Supp.Fig.5-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.5-PAX3.pdf")


```


**Figure S5.** MFE [Minimum Free Energy] values in optimised and native sequences of the *KIT* and *PAX3* genes

\newpage






```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

knitr::include_graphics("supplemetary_figures/Supp.Fig.6-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.6-PAX3.pdf")


```

**Figure S6.**  Heatmap of longest consecutive A/C/T/G tracts in optimised sequences of the *KIT* and *PAX3* genes.

\newpage




## RNAi (siRNA/shRNA) prediction



```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.7-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.7-PAX3.pdf")


```

**Figure S7.** Counts of self-complementary regions in predicted RNAi sequences targeting the *KIT* and *PAX3* genes.



\newpage


```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.8-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.8-PAX3.pdf")


```



**Figure S8.** GC content [%] in predicted RNAi sequences targeting the *KIT* and *PAX3* genes.


\newpage




```{r out.width="80%", fig.align='center', include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_graphics("supplemetary_figures/Supp.Fig.9-KIT.pdf")
knitr::include_graphics("supplemetary_figures/Supp.Fig.9-PAX3.pdf")


```


**Figure S9.** Nucleotide positions score in predicted RNAi sequences targeting the *KIT* and *PAX3* genes based on series of publications: DOI:10.1093/nar/gkn902; DOI:10.1093/nar/gkh247; DOI:10.1038/nbt936;; DOI:10.1016/j.bbrc.2004.02.157




<!--
rmarkdown::render("supplementary.Rmd",
                  output_format = "pdf_document",
                  output_file = "supplementary.tex",
                  clean = FALSE)
-->
